---
title: "Lead Times for Lead"
author: "Stephen D. Wells"
date: "September 22, 2015"
output: ioslides_presentation
runtime: shiny
---

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Slide with Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Lead Times for Lead

```{r, echo=FALSE}
library(leaflet)
library(maps)
library(RColorBrewer)

colors <- heat.colors(20, alpha=1)
#colors <- rep("red",20)
#colors <- topo.colors(20, alpha=1)
colors <- substring(colors,1,7)


lead=read.csv("./StateConfirmedByYear_1997_2013_03042015.csv")
stateConversions=read.csv("StateConversions.csv")
homicide_wide=read.csv("./homicide_wide.csv")

shiftedCorr <- function(dataFrame1,dataFrame2,colName1="PctConfirmedBllGT10",colName2="Overall",yearDelta=0,stateConv) {
  dataFrame1$State <- as.character(dataFrame1$State)
  dataFrame2$State <- as.character(dataFrame2$State)
  dataFrame1$Year=dataFrame1$Year+yearDelta
  mergeDF<-merge(dataFrame1,dataFrame2,by=c('Year', 'State'))
  mergeDF <- mergeDF[,c("Year","State",colName1,colName2)]
  mergeDF <- na.omit(mergeDF)
  stateLIST <- unique(mergeDF$State)
  numStates <- length(stateLIST)
  leadCrimeCorr <- NULL
  for ( s in 1:numStates ) {
    print(s)
    theState <- stateLIST[s]
    subDF <- mergeDF[ mergeDF$State == theState, ]
    if ( nrow(subDF) > 0 ) {
    subDF2 <- stateConv[ stateConv$State == tolower(theState), ]
    subDF2$Corr <-cor(subDF[,colName1], subDF[,colName2], use="complete.obs")
    leadCrimeCorr <- rbind(leadCrimeCorr,subDF2)
  }
  }
  return(leadCrimeCorr)
}

inputPanel({
 sliderInput("delta", "Delta:", 
                min = 0, max = 4, value = 0, step=1)
})

renderLeaflet({
  data = shiftedCorr(lead, homicide_wide, "PctConfirmedBllGT10","Overall",input$delta,stateConversions)
  data$CorrInt <- ceiling(data$Corr*10 + 10)
  data$Color <- colors[ data$CorrInt ]
  mapStates = map("state", fill=TRUE, plot=TRUE)

  state_names <- mapStates$names
  
 state_col <- rep("#FFFFFF", length(state_names))
 names(state_col) <- state_names
#  state_col["nebraska"] <- "#00FF00"
#  names(state_col) <- NULL
  
  stateLIST <- as.character(data$OLDSTATE)
  numStates <- length(stateLIST)

  for ( i in 1:numStates ) {
    theState <- stateLIST[i]
    theColor <- data$Color[ data$OLDSTATE == theState ]
    state_col[ theState ] <- theColor
  }
  names(state_col) <- NULL
  print(state_col)
  
#  popup_col <- rep('', length(state_names))
#  names(popup_col) <- state_names
#  popup_col["nebraska"] <- "Nebraska"
#  names(popup_col) <- NULL
  
  m = leaflet(data = mapStates) %>%
        addTiles() %>%
        addPolygons(fillColor = state_col, stroke = FALSE)
  #                  popup=as.character(1:63))
  
  
  #addPolygons(fillColor = state_col, stroke = FALSE)
  
  #addPolygons(fillColor = topo.colors(10, alpha = NULL), stroke = FALSE)
        #print(heat.colors(50, alpha = NULL))
        
  return(m)
})
```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```


